Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-09-15 psy_peds.Rmd
correcting time series analysis plots

```{r}
# Time series analysis of percentage of psy codes per encounter, linear (without seasonality)
ts_linear_percent <- lm(percentage ~ period * time, patient_count_monthly_psy)
time_serie_analysis_plotting(ts_linear_percent, patient_count_monthly_psy) + 
    labs(title = "Interrupted Time-Serie Analysis: Percentage of encounters with psychiatric ICD codes", 
         subtitle = "Without seasonality effect",
         x = "Percentage", 
         y = "Month")
ggsave("output/time_series_percent_linear.png", width = 18, height = 9, units="cm")

@@

```{r}
# Time series analysis of percentage of psy codes per encounter, with seasonality
ts_seasonal_percent <- lm(percentage ~ period*time + harmonic(month_year, 2, 12), patient_count_monthly_psy)
time_serie_analysis_plotting(ts_seasonal_percent, patient_count_monthly_psy) +
  labs(title = "Interrupted Time-Serie Analysis: Percentage of encounters with psychiatric ICD codes", 
       subtitle = "With seasonality effect",
       x = "Percentage", 
       y = "Month")
ggsave("output/time_series_percent_seasonal.png", width = 18, height = 9, units="cm")

@@

pred_ts_seasonal_count <- bind_cols(patient_count_monthly_psy, pred_ts_seasonal_count, pred_ts_seasonal_count_b)
ggplot(pred_ts_seasonal_count, aes(x = month, y = patients_per_category)) + 
  geom_point() +
  geom_line(aes(x = month, y = fit, colour = "Mean pandemic")) +
  geom_line(aes(x = month, y = fit_wo_intervention, colour = "Expected mean w/o pandemic"), linetype = "dashed") + 
  scale_color_manual(name = "Time Series projection", values = c("Mean pandemic" = "black", "Expected mean w/o pandemic" = "red")) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  annotate("text", x = as.Date("2019-10-01"), y = max(pred_ts_seasonal_count$patients_per_category) + 5, label = annotation) +
  labs(title = "Interrupted Time-Serie Analysis: Count of encounters with psychiatric ICD codes", 
       subtitle = "With seasonality effect",
       x = "Percentage", 
       y = "Month") + 
  theme(legend.position = "bottom")
ggsave("output/time_series_count_seasonal.png", width = 18, height = 9, units="cm")
```

>>>>

```{r}
# Time series analysis of percentage of psy codes per encounter, linear (without seasonality)
ts_linear_percent <- lm(percentage ~ period * time, patient_count_monthly_psy)
time_serie_analysis_plotting(ts_linear_percent, patient_count_monthly_psy) + 
    labs(title = "Interrupted Time-Serie Analysis: Percentage of encounters with psychiatric ICD codes", 
         subtitle = "Without seasonality effect",
         x = "Month", 
         y = "Percentage")
ggsave("output/time_series_percent_linear.png", width = 18, height = 9, units="cm")

@@

```{r}
# Time series analysis of percentage of psy codes per encounter, with seasonality
ts_seasonal_percent <- lm(percentage ~ period*time + harmonic(month_year, 1, 12), patient_count_monthly_psy)
time_serie_analysis_plotting(ts_seasonal_percent, patient_count_monthly_psy) +
  labs(title = "Interrupted Time-Serie Analysis: Percentage of encounters with psychiatric ICD codes", 
       subtitle = "With seasonality effect",
       x = "Month", 
       y = "Percentage")
ggsave("output/time_series_percent_seasonal.png", width = 18, height = 9, units="cm")

@@

pred_ts_seasonal_count <- bind_cols(patient_count_monthly_psy, pred_ts_seasonal_count, pred_ts_seasonal_count_b)
ggplot(pred_ts_seasonal_count, aes(x = month, y = patients_per_category)) + 
  geom_point() +
  geom_line(aes(x = month, y = fit, colour = "Mean pandemic")) +
  geom_line(aes(x = month, y = fit_wo_intervention, colour = "Expected mean w/o pandemic"), linetype = "dashed") + 
  scale_color_manual(name = "Time Series projection", values = c("Mean pandemic" = "black", "Expected mean w/o pandemic" = "red")) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  annotate("text", x = as.Date("2019-10-01"), y = max(pred_ts_seasonal_count$patients_per_category) + 5, label = annotation) +
  labs(title = "Interrupted Time-Serie Analysis: Count of encounters with psychiatric ICD codes", 
       subtitle = "With seasonality effect",
       x = "Month", 
       y = "Count") + 
  theme(legend.position = "bottom")
ggsave("output/time_series_count_seasonal.png", width = 18, height = 9, units="cm")
```
